---
title: "C API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{C API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(colorfast)
```

`{colorfast}` exports three C functions for use in other packages.

To use these functions:

* In your package `DESCRIPTION`
    * Add `LinkingTo: colorfast` 
    * Add `Depends: colorfast (>= 1.0.0.9000)`
* In your C code
    * Add `#include <colorfast.h>`
    * Call the functions below

```
void col_to_rgb(const char *col, int ptr[4]);
uint32_t col_to_int(const char *col); 
void int_to_col(uint32_t icol, char buf[10]);
```


## String colour to vector of RGBA values 

`void col_to_rgb(const char *col, int ptr[4])`

The following is equivalent to: `col_to_rgb('red')`

``` c
#include <colorfast.h>

void custom_c_function(const char *col) {
  int values[4];
  col_to_rgb(col, values);
  ...
}
```



## String colour to packed integer colour 

`void col_to_int(const char *col)`

The following is equivalent to: `col_to_int('red')`

``` c
#include <colorfast.h>

void custom_c_function(const char *col) {
  uint32_t value = col_to_int(col);
  ...
}
```


## String colour to packed integer colour 

`void col_to_int(const char *col)`

The following is equivalent to: `int_to_col(123877L)`

``` c
#include <colorfast.h>

void custom_c_function(uint32_t icol) {
   char buf[10]
   int_to_col(icol, buf);
  ...
}
```









